\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-20 chapters/supplementary.tex
Update figs; add extended CS results

\textbf{Left:} Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction. \textbf{Right:} The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters. \TODO{Update notation figure}}

@@

\paragraph*{Complexity} In the main loop, the algorithm iterates over all edges, but the only iterations presenting a complexity different from $\mathcal{O}(1)$ are the ones involving a merge of two clusters, which are at most $N-1$. By using a union-find data structure (with path compression and union by rank) the time complexity of \texttt{merge}$(u, v)$ and \texttt{find}($u$) operations is $\mathcal{O}(\alpha(N))$, where $\alpha$ is the slowly growing inverse Ackerman function. The algorithm then iterates over the neighbors of the merged cluster (at most $N$) and updates/deletes values in the priority queue ($\mathcal{O}(\log |E|)$). Therefore, similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$. In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory. Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$. 
% and \UPDATE{in Fig. \ref{fig:runtime_plot} we show how the empirical runtime of \algname{} is much closer to $\mathcal{O}(N \log N)$ than $\mathcal{O}(N^2 \log N)$.} 
With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$. 
Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity. \TODO{Empirical complexity plot?}

@@

\subsection{Neuron segmentation and compared methods}\label{sec:cremi_details}
\paragraph{Training details} The data from the CREMI challenge is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds. 
To alleviate difficulties stemming from misalignment, we use a version of the data that was elastically realigned by the challenge organizers with the method of \cite{saalfeld2012elastic}.
We train a 3D U-Net \cite{ronneberger2015u, cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and  elastic deformations, we simulate data artifacts.
In more detail, we randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data. Both \cite{funke2018large} and \cite{lee2017superhuman} have shown
that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
We use L2 loss and Adam optimizer to train the network. \TODO{Field of view?}

@@

\subsection{\algname{} on the full CREMI dataset} \label{sec:appendix_exps_full_cremi}
 \paragraph{Pre-merge processing} For the predictions on the full dataset from the CREMI challenge, we used  the padded volumes provided by the challenge. The crops on which we performed a prediction have a size of $1500\times1500\times127=2.86\cdot 10^8$ voxels or larger. Building a graph with $10^8$ nodes can easily incur a large use of memory, so we decided to perform a preprocessing step by initially merging some nodes together. Simply down-sampling the predictions of the CNN would have led to a loss of resolution and performances in the most difficult parts of the dataset. Thus, we decided to pre-merge the most connected components of the graph that would be anyway clustered during the first iterations of \algname{}. To do this, we used a simple approach: we generated a boundary probability map by taking for each voxel an average over affinities in all directions (both short- and long-range ones) and we run THRESH to find the connected components. With this approach, pixels are pre-clustered only when they are far away (in all directions) from all predicted boundaries. 
 To make sure that in this preprocessing step different neurons are never merged together by mistake, we intersected these segments given by the conservative THRESH with the segments given by WSDT \TODO{show figure?}. By using this method, we initialized \algname{} with a reduced graph that represents a true over-segmentation. In our experiments, the use of this preprocessing method did not impact the final scores achieved by \algname{} and significantly reduced its runtime. On the full datasets, we used only 10 \% of the long-range connections in the pixel-graph, since adding all of them did not improve the scores and only made the simulations much slower and memory inefficient.

@@

\begin{figure}[b]
\centering
        \includegraphics[width=0.45\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}

    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}). \TODO{Add raw-data (and GT)}
    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
    }
    \label{fig:noisy_affs}
\end{figure}

@@

Before to apply \algname{}, we performed a parameter-search for the bias $\beta$ defined in \ref{eq:mappings}. Table \ref{tab:results_cityscapes_val_expanded} lists the best-case performances for each of the methods with the chosen bias $\beta$: note that depending on the version of \algname{}, it was necessary to bias more or less the predicted edge weights. \TODO{Add extended table (explain what $\beta=0$ means)}

>>>>

\textbf{Left:} Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction. \textbf{Right:} The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.}

@@

\paragraph*{Complexity} In the main loop, the algorithm iterates over all edges, but the only iterations presenting a complexity different from $\mathcal{O}(1)$ are the ones involving a merge of two clusters, which are at most $N-1$. By using a union-find data structure (with path compression and union by rank) the time complexity of \texttt{merge}$(u, v)$ and \texttt{find}($u$) operations is $\mathcal{O}(\alpha(N))$, where $\alpha$ is the slowly growing inverse Ackerman function. The algorithm then iterates over the neighbors of the merged cluster (at most $N$) and updates/deletes values in the priority queue ($\mathcal{O}(\log |E|)$). Therefore, similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$. In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory. Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$. 
% and \UPDATE{in Fig. \ref{fig:runtime_plot} we show how the empirical runtime of \algname{} is much closer to $\mathcal{O}(N \log N)$ than $\mathcal{O}(N^2 \log N)$.} 
With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$. 
Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity. %\TODO{Empirical complexity plot?}

@@

\subsection{Neuron segmentation and compared methods}\label{sec:cremi_details}
\paragraph{Training details} The data from the CREMI challenge is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds. 
To alleviate difficulties stemming from misalignment, we use a version of the data that was elastically realigned by the challenge organizers with the method of \cite{saalfeld2012elastic}.
We train a 3D U-Net \cite{ronneberger2015u, cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and  elastic deformations, we simulate data artifacts.
In more detail, we randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data. Both \cite{funke2018large} and \cite{lee2017superhuman} have shown
that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
We use L2 loss and Adam optimizer to train the network. % \TODO{Field of view?}

@@

\subsection{\algname{} on the full CREMI dataset} \label{sec:appendix_exps_full_cremi}
 \paragraph{Pre-merge processing} For the predictions on the full dataset from the CREMI challenge, we used  the padded volumes provided by the challenge. The crops on which we performed a prediction have a size of $1500\times1500\times127=2.86\cdot 10^8$ voxels or larger. Building a graph with $10^8$ nodes can easily incur a large use of memory, so we decided to perform a preprocessing step by initially merging some nodes together. Simply down-sampling the predictions of the CNN would have led to a loss of resolution and performances in the most difficult parts of the dataset. Thus, we decided to pre-merge the most connected components of the graph that would be anyway clustered during the first iterations of \algname{}. To do this, we used a simple approach: we generated a boundary probability map by taking for each voxel an average over affinities in all directions (both short- and long-range ones) and we run THRESH to find the connected components. With this approach, pixels are pre-clustered only when they are far away (in all directions) from all predicted boundaries. 
 To make sure that in this preprocessing step different neurons are never merged together by mistake, we intersected these segments given by the conservative THRESH with the segments given by WSDT. %\TODO{show figure?}
 By using this method, we initialized \algname{} with a reduced graph that represents a true over-segmentation. In our experiments, the use of this preprocessing method did not impact the final scores achieved by \algname{} and significantly reduced its runtime. On the full datasets, we used only 10 \% of the long-range connections in the pixel-graph, since adding all of them did not improve the scores and only made the simulations much slower and memory inefficient.

@@

\begin{figure}[b]
\end{figure}

% \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
%  &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
% % Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
% % \multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
%  % &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
% \multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
%  &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
% \multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
%  &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
% \cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
\begin{figure}[t]
\centering
\begin{minipage}[T]{0.35\textwidth}
    \centering
    \footnotesize
        \begin{tabular}{l|c|c}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          % Pipeline & method & \textsc{No} & \textsc{Yes} \\ 
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster.}
    \label{tab:extended_results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[T]{0.6\textwidth}
\centering
        \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}). \TODO{Overlay raw-data}
    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
    }
    \label{fig:noisy_affs}
\end{minipage}
\end{figure}

@@

Before to apply \algname{}, we performed a parameter-search for the bias $\beta$ defined in \ref{eq:mappings}. Table \ref{tab:extended_results_cityscapes_val} lists the best-case performances for each of the methods with the chosen bias $\beta$: note that depending on the version of \algname{}, it was necessary to bias more or less the predicted edge weights.
